\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-26 paper/mswp2012-proposal.tex
More information about UCD

\subsection{User Centered Design}
We chose \emph{User Centered Design} as the procedure model used for the modern health care system. We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system. User Centered Design is an iterative process that aims at supporting this procedure by integrating the user into the design process. By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work. User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods to emphasize functionality and robustness of systems. User Centered Design runs through 4 phases [see figure \ref{fig:UCD}]:

@@

\begin{figure}[htb]
	\centering
		\includegraphics[width=1\textwidth]{images/UCD.pdf}
	\caption{User Centered Design}
	\label{fig:UCD}
\end{figure}

>>>>

\subsection{User Centered Design}
We decided on \emph{User Centered Design} as the procedure model used to accompany the creation of the Modern Health Care System. We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system. User Centered Design is an iterative process that aims at supporting this procedure by integrating the user early into the design process. By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work. User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods that more often emphasize on functionality and robustness of the system. \\

User Centered Design runs through 4 phases [see figure \ref{fig:UCD}]:

@@

\begin{figure}[htb]
	\centering
		\includegraphics[width=1\textwidth]{images/UCD.pdf}
	\caption{User Centered Design Process}
	\label{fig:UCD}
\end{figure}

During the \emph{Research Phase} information about the users, their profiles and their needs is collected. During the \emph{Design Phase} the requirements are specified based on the information gathered in the research phase and the concepts are created. During the \emph{Prototyping Phase} various forms of mockups and prototypes are created based on the information gathered in the design phase. In the \emph{Evaluation Phase} the prototypes and mockups are finally discussed with the users and evaluated. It is important to repeatedly check if the needs of the users are still met. Therefore the phases are interconnected and fast iteration is a vital part of User Centered Design.
